---
title: "E13.5 P7 WGCNA"
output: html_notebook
---

Here I generate genemodules using the weighted gene co-expression analysis approach with the r package WGCNA
First we load the single-cell data set to perform the analysis on.
Loading the E13.5 and P7 data in R
```{r, include=FALSE}
setwd("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7")
file_names_expression=as.list(dir(path = "data/",pattern="*_expression_for_R.tab"))
file_names_annotation=as.list(dir(path = "data/",pattern="*_MATLAB_annotations.tab"))

library(dplyr)
library(plyr)
library(biomaRt)
library(scde)
library(igraph)
library(ggplot2)

setwd("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/data")
expressions <- lapply(file_names_expression,read.table,header=TRUE, sep="\t", as.is=TRUE, check.names=FALSE)
names(expressions) <- file_names_expression
list2env(expressions,environment())
row.names_expressions <- expressions[[1]][,1]
rm(list = as.character(names(expressions)))
expressions <- lapply(expressions,`[`,-1)
names(expressions) <- file_names_expression
expressions <- do.call(cbind,expressions)
row.names(expressions) <- row.names_expressions

annotations <- lapply(file_names_annotation,read.table,header=TRUE, sep="\t", as.is=TRUE, check.names=FALSE)
names(annotations) <- file_names_annotation
list2env(annotations,environment())
row.names_annotations <- annotations[[1]][,1]
rm(list = as.character(names(annotations)))
annotations <- lapply(annotations,`[`,-1)
names(annotations) <- file_names_annotation
annotations <- do.call(cbind,annotations)
row.names(annotations) <- row.names_annotations
rm(list=ls(pattern="row.names_"))
setwd("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7")

idx <- !duplicated(t(annotations))
annotations <- t(annotations)
annotations <- as.data.frame(annotations[idx,]) # remove duplicated rows

annotations$Sample <- as.factor(annotations[,'Plate'])
annotations$Sample <- revalue(annotations$Sample, c("1771-048-203"="P7-Brain", "1771-048-224"="P7-Brain","1771-051-143"="P7-Spinal-Cord-old","1771-051-152"="E13.5-Brain", "1771-051-162"="E13.5-Brain",
                                                    "1771-055-004"="E13.5-Brain","1771-055-005"="E13.5-Brain","1771-055-006"="E13.5-Brain","1771-055-007"="E13.5-Spinal-Cord",
                                                    "1771-055-008"="P7-Spinal-Cord","1772-122-163"="E13.5-Brain","1772-122-164"="E13.5-Spinal-Cord","1772-122-165"="E13.5-Spinal-Cord","1772-122-239"="E13.5-Spinal-Cord",
                                                    "1772-122-241"="P7-Spinal-Cord","1772-122-243"="P7-Spinal-Cord","1772-122-244"="P7-Spinal-Cord"))
levels(annotations$Sample)
emat <- expressions[,idx]
rm(expressions,file_names_annotation,file_names_expression,idx)
#write.table(emat,file = "E13.5_P7_expression.txt", sep="\t",row.names = TRUE, col.names = TRUE)
#write.table(annotations,file = "E13.5_P7_annotation.txt", sep="\t",row.names = TRUE, col.names = TRUE)
colnames(emat) <- rownames(annotations)
#emat[1:10,1:4] # Inspect the data...

ERCC <- subset(emat, grepl("ERCC-*", row.names(emat)))
emat_saved <- emat

#Convert to gencode using biomart
listMarts()
ensembl = useMart("ensembl",dataset="mmusculus_gene_ensembl")
listDatasets(ensembl)
attributes = listAttributes(ensembl)
Biomart_gencode_ensembl84_biotypes <- getBM(attributes=c("mgi_symbol","ensembl_gene_id","gene_biotype"), filters = "", values = "", ensembl)
Biomart_gencode_ensembl84_biotypes[, 'gene_biotype'] <- as.factor(Biomart_gencode_ensembl84_biotypes[,'gene_biotype'])
#Filter for only our genes
Biotype_All_dataset <- subset(Biomart_gencode_ensembl84_biotypes, mgi_symbol %in% row.names(emat_saved))

emat <- subset(emat_saved, !grepl("ERCC-*", row.names(emat)))
Mitochondrial <- subset(Biotype_All_dataset$mgi_symbol, grepl("Mt_*", Biotype_All_dataset$gene_biotype))
Mitochondrial <- emat[Mitochondrial,]
ERCC_counts <- as.numeric(apply(ERCC, 2, sum))
total_Spikein <- as.numeric(as.vector(annotations$SpikeMolecules))
Mitochondrial_counts <- as.numeric(apply(Mitochondrial, 2, sum))
total_counts <- as.numeric(apply(emat,2,sum))
QC <- as.data.frame(cbind(ERCC_counts,total_Spikein,total_counts,Mitochondrial_counts))
QC$CaptureEfficiency <- (QC$ERCC_counts / QC$total_Spikein)
QC$PercOfReadMappedToSpikein <- (QC$ERCC_counts / QC$total_counts)
QC[is.na(QC)] <- 0
QC <- as.matrix(QC)
QC[is.infinite(QC)] <- 0
QC <- as.data.frame(QC)
QC$NormalizedCounts <- round((QC$total_counts * QC$CaptureEfficiency),0)
row.names(QC) <- row.names(annotations)
emat <- emat_saved

#Now we load the backSPIN annotation file
backSPIN <-  read.delim("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/data/backSPIN_E13P7_2016.txt",
header=FALSE, sep="\t", as.is=TRUE,check.names=FALSE)
backSPIN[1,] <- c("cellid","clusters","annotation")
colnames(backSPIN) <- backSPIN[1,]
backSPIN <- backSPIN[-1,]
row.names(backSPIN) <- backSPIN[,1]
annotable_backSPIN <- annotations
annotable_backSPIN$cellid <- apply(annotable_backSPIN,1,function(x){paste(x[3],x[1],sep = "_")})
annotable_backSPIN$cellid <- gsub("-", "", annotable_backSPIN$cellid, fixed = TRUE)
annotable_backSPIN <- subset(annotable_backSPIN, row.names(annotable_backSPIN) %in% colnames(emat))
annotable_backSPIN <- subset(annotable_backSPIN, cellid %in% row.names(backSPIN))
backSPIN <- backSPIN[annotable_backSPIN$cellid,]
annotable_backSPIN$backSPINclust <- backSPIN$clusters
annotable_backSPIN$backSPINanno <- backSPIN$annotation

annotable_backSPINcleaned <- subset(annotable_backSPIN,! backSPINanno %in% "" )

backSPIN <- annotable_backSPINcleaned[,14]
names(backSPIN) <- row.names(annotable_backSPINcleaned)
backSPINnoisy <- subset(annotable_backSPIN,backSPINanno %in% c(""))[,14]
names(backSPINnoisy) <- row.names(subset(annotable_backSPIN,backSPINanno %in% c("")))
xSPIN = character()
for(i in 1:nrow(annotations)) {if(any(row.names(annotations[i,])==names(backSPINnoisy))) {xSPIN[i] <- 1} else{xSPIN[i] <- 0}}
xSPIN <- as.factor(xSPIN)
table(xSPIN)
```
```{r}
# Load the WGCNA package
library(WGCNA);
# The following setting is important, do not omit.
options(stringsAsFactors = FALSE);
allowWGCNAThreads()
E13P7_expr <- emat_backSPIN
E13P7_expressed <- apply(E13P7_expr,1,function(x) any ((x) >= 5))
E13P7_expr <- t(log(E13P7_expr[E13P7_expressed,]+1))
gsg = goodSamplesGenes(E13P7_expr, verbose = 3);
gsg$allOK

if (!gsg$allOK)
{
# Optionally, print the gene and sample names that were removed:
if (sum(!gsg$goodGenes)>0)
printFlush(paste("Removing genes:", paste(names(E13P7_expr)[!gsg$goodGenes], collapse = ", ")));
if (sum(!gsg$goodSamples)>0)
printFlush(paste("Removing samples:", paste(rownames(E13P7_expr)[!gsg$goodSamples], collapse = ", ")));
# Remove the offending genes and samples from the data:
E13P7_expr = E13P7_expr[gsg$goodSamples, gsg$goodGenes]
}
sampleTree = hclust(dist(E13P7_expr), method = "average");
plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2,labels = FALSE)
# Plot a line to show the cut
abline(h = 62.5, col = "red");
# Determine cluster under the line
clust = cutreeStatic(sampleTree, cutHeight = 62.5, minSize = 10)
table(clust)
# clust 1 contains the samples we want to keep.
keepSamples = (clust==1)
datExpr = E13P7_expr#[keepSamples, ]
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)
```
```{r}
# Choose a set of soft-thresholding powers
powers = c(c(1:10), seq(from = 12, to=20, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(log(datExpr+1), powerVector = powers, verbose = 5)
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=1,col="red")
```
```{r}
softPower <- 3;
adjacency = adjacency(datExpr, power=softPower);
# Turn adjacency into topological overlap
TOM = TOMsimilarity(adjacency);
dissTOM = 1-TOM
# Call the hierarchical clustering function
geneTree = hclust(as.dist(dissTOM), method = "average");
# Plot the resulting clustering tree (dendrogram)
plot(geneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
labels = FALSE, hang = 0.04);
```

```{r}
# We like large modules, so we set the minimum module size relatively high:
minModuleSize = 20;
# Module identification using dynamic tree cut:
dynamicMods = cutreeDynamic(dendro = geneTree, distM = dissTOM,
deepSplit = 2, pamRespectsDendro = FALSE,
minClusterSize = minModuleSize);
table(dynamicMods)

# Convert numeric lables into colors
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")
```
```{r}
# Calculate eigengenes
MEList = moduleEigengenes(datExpr, colors = dynamicColors)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(METree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
MEDissThres = 0.25
# Plot the cut line into the dendrogram
abline(h=MEDissThres, col = "red")
# Call an automatic merging function
merge = mergeCloseModules(datExpr, dynamicColors, cutHeight = MEDissThres, verbose = 3)
# The merged module colors
mergedColors = merge$colors;
# Eigengenes of the new merged modules:
mergedMEs = merge$newMEs;
# Plot with old and merged clusters
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
# Rename to moduleColors
moduleColors = mergedColors
# Construct numerical labels corresponding to the colors
colorOrder = c("grey", standardColors(50));
moduleLabels = match(moduleColors, colorOrder)-1;
MEs = mergedMEs;
```
```{r, fig.height=5}
Eigengenedata <- as.data.frame(MEList$eigengenes)
row.names(Eigengenedata) <- row.names(annotable_backSPIN)
library(heatmap3)
heatmap3(Eigengenedata, Rowv = NULL , Colv = NA ,scale = "row",filterFun = sd, method = "average",col=colorRampPalette(c("red","black","green"))(1024))

ADJ1=abs(cor(datExpr,use="p"))^3
Alldegrees1=intramodularConnectivity(ADJ1, mergedColors)
head(Alldegrees1)

datKME=signedKME(datExpr, MEs, outputColumnName="MM.")
# Display the first few rows of the data frame
head(datKME)
write.table(datKME, file = "~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/KME.txt", sep = "\t")

#Convert to gencode using biomart
listMarts()
ensembl = useMart("ensembl",dataset="mmusculus_gene_ensembl")
listDatasets(ensembl)
attributes = listAttributes(ensembl)
Biomart_gencode_ensembl84_biotypes <- getBM(attributes=c("mgi_symbol","ensembl_gene_id","entrezgene","gene_biotype"), filters = "", values = "", ensembl)
Biomart_gencode_ensembl84_biotypes[, 'gene_biotype'] <- as.factor(Biomart_gencode_ensembl84_biotypes[,'gene_biotype'])
#Filter for only our genes
Biotype_All_dataset <- subset(Biomart_gencode_ensembl84_biotypes, mgi_symbol %in% row.names(emat_backSPIN))
entrezID <-  subset(Biotype_All_dataset, Biotype_All_dataset$mgi_symbol %in% row.names(emat_backSPIN))
entrezmatched <- entrezID[match(colnames(datExpr),entrezID$mgi_symbol),]
entrezID <- entrezID[! apply(entrezID[,c(1,3)], 1,function (x) anyNA(x)),]
allLLIDs <- entrezmatched$entrezgene

GOenr = GOenrichmentAnalysis(moduleColors, allLLIDs, organism = "mouse", nBestP = 50);
tab = GOenr$bestPTerms[[4]]$enrichment
write.table(tab, file = "~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/tab.txt", sep = "\t")

```




```{r}
exp.m <- t(datExpr)
ppiA.m <- 1*(ADJ1 > mean(ADJ1))
pheno.v <- annotable_backSPINcleaned[,14]
names(pheno.v) <- row.names(annotable_backSPINcleaned)
# First integrate exp.m and ppiA.m:
int.o <- DoIntegPPI(exp.m,ppiA.m)
# Now estimate maximum SR:
maxSR <- CompMaxSR(int.o$adjMC);
#Now estimate signaling entropies of all samples
SR.v <- vector(); for(s in 1:ncol(exp.m))
  { SR.v[s] <- CompSRana(int.o$expMC[,s],int.o$adjMC,maxSR=maxSR)$sr; print(paste(100*(s/(ncol(exp.m)))));}
#Now perform SCENT:
scent.o <- DoSCENT(exp.m,sr.v=SR.v,pheno.v)
#Define bulk expression profile
expBLK.v <- rowMeans(int.o$expMC);
#Compute SR for bulk
SRblk <- CompSRana(expBLK.v,int.o$adjMC,maxSR=maxSR)
#Estimate MRH:
mrh.o <- EstMRH(SR.v,SRblk$sr);
View(scent.o$hetPS)
plot(density(scent.o$distPSPH))
```


First let's test if any principal components are correlating with the mean count.
```{r}
WGCNA_highMM <- row.names(subset(Alldegrees1, Alldegrees1$kWithin > 5))
pca <- prcomp(datExpr[,WGCNA_highMM],scale. = FALSE)
genecount <- rowSums(datExpr[,WGCNA_highMM])
genecountcor <- cor(genecount,pca$x[,c(1)])
plot(genecount,pca$x[,c(1)],pch=20,cex=0.5,main=c("R",round(genecountcor,2)))
line <- line(genecount,pca$x[,c(1)])
abline(line, col="red")
```



Lets run the tSNE and remove PC1 because it correlates with the genecount
```{r, message=FALSE, warning=FALSE, include=FALSE}
#tsne <- log(emat.normalized[NormGenes,names(backSPIN)]+1)
pca <- prcomp(datExpr[,WGCNA_highMM],scale. = FALSE)
tsne <- t(pca$x[,c(2:20)])
library(Rtsne)
set.seed(123456789)
tsne_out <- Rtsne(t(tsne), initial_dims=20, perplexity=60,max_iter = 1000,check_duplicates = FALSE,
                  verbose = TRUE, theta = 0.0, pca = FALSE)
rownames(tsne_out$Y) <- colnames(tsne)
```

```{r, echo=FALSE, fig.height=5}
FinalClustersOrdered <- factor(annotable_backSPIN$FinalClusters, levels=c("OPC1","OPC2","OPC3","COP","NFOL","Cycling","NP1a","NP1b","NP2","NP3","eVLMC","PLC","pnVLMC","VLMC"))
palette <- c("#c6dbef","#6baed6","#08519c","#006d2c","#41ab5d","#000000","#cab2d6","#6a3d9a","#dadaeb","#c994c7","#fcbba1","#ef3b2c","#a63603","#f16913")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=FinalClustersOrdered)) +
  geom_point(size=3) + geom_density2d(alpha=0.0,size=0.1, color="black", bins=10)  + (scale_colour_manual(FinalClustersOrdered,values=palette)) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")  +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.border = element_blank(),
       panel.background = element_blank())
```
```{r, echo=FALSE}
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=FinalClustersOrdered)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.1, color="black", bins=10)  + (scale_colour_manual(FinalClustersOrdered,values=palette)) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")  +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.border = element_blank(),
       panel.background = element_blank())
#Show Genemodules
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEblack)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEblue)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEbrown)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEcyan)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
  ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEgreen)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEgreenyellow)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEgrey)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEgrey60)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MElightcyan)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEmagenta)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEmidnightblue)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEpink)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEpurple)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEred)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEsalmon)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEtan)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEturquoise)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Eigengenedata$MEyellow)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
```

Get TFs from modules
```{r, fig.height=3}
library(heatmap3)
FinalClustersOrdered <- factor(annotable_backSPIN$FinalClusters, levels=c("OPC1","OPC2","OPC3","COP","NFOL","Cycling","NP1a","NP1b","NP2","NP3","eVLMC","PLC","pnVLMC","VLMC"))
palette <- c("#c6dbef","#6baed6","#08519c","#006d2c","#41ab5d","#000000","#cab2d6","#6a3d9a","#dadaeb","#c994c7","#fcbba1","#ef3b2c","#a63603","#f16913")
#COP Cycling    NFOL    NP1a    NP1b     NP2     NP3    OPC1    OPC2    OPC3     PLC    VLMC   eVLMC  pnVLMC 
palette <- c("#006d2c","#000000","#41ab5d","#cab2d6","#6a3d9a","#dadaeb","#c994c7","#c6dbef","#6baed6","#08519c","#ef3b2c","#f16913","#fcbba1","#a63603")
table(annotable_backSPIN$FinalClusters)
cols <- palette[as.factor(annotable_backSPIN$FinalClusters)]
heatmap3(t(Eigengenedata),ColSideColors=cols, Rowv = NA , Colv = NULL ,scale = "col",filterFun = sd, method = "ward.D2",col=colorRampPalette(c("#2c7bb6","#ffffbf",
"#d7191c"))(1024),balanceColor = T)

TFlist <- read.table("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/MarkersSCDE/TFlist.txt")
TFlist <- TFlist$V1
ChMlist <- read.table("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/MarkersSCDE/ChMlist.txt")
ChMlist <- ChMlist$V1
CoFactorslist <- read.table("~/Documents/SingleCellData/GitCloneWABI/E13.5-P7/MarkersSCDE/CoFactorslist.txt")
CoFactorslist <- CoFactorslist$V1
AllTfsList <- union(union(TFlist,ChMlist),CoFactorslist)

datKMETFs <- datKME[AllTfsList,]

```
```{r, echo=FALSE}
#Show Entropy score
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=SR.v)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
```

We create a PPI network from the iRef online database
```{r}
#Now we get a PPI interactome network to work with

library("iRefR")
iref = get_irefindex(tax_id="10090",iref_version="13.0",data_folder="~/Documents/SingleCellData/")
mouse_mouse_list = data.frame(iref$taxa,iref$taxb)
tmp = do.call(`paste`, c(unname(mouse_mouse_list), list(sep=".")))
iref_mouse = iref[tmp == "taxid:10090(Mus musculus).taxid:10090(Mus musculus)" | tmp == "-.taxid:10090(Mus musculus)",]

library(stringr)
mA = str_locate(iref_mouse$aliasA, perl("hgnc:.*?\\|"))
hugoA = str_sub(iref_mouse$aliasA,mA[,1]+5,mA[,2]-1)
mB = str_locate(iref_mouse$aliasB, perl("hgnc:.*?\\|"))
hugoB = str_sub(iref_mouse$aliasB,mB[,1]+5,mB[,2]-1)
x = data.frame(iref_mouse$X.uidA,iref_mouse$uidB,hugoA,hugoB,iref_mouse$irigid)
colnames(x) = c("uidA","uidB","hugoA","hugoB","irigid")
dim(x)

v = unique(data.frame(c(as.character(x$uidA),as.character(x$uidB)),c(as.character(x$hugoA),as.character(x$hugoB))))
colnames(v) = c("uid","hugo")
x <- x[,3:4]
y <- apply(x,1,function(x) any(is.na(x)))
x <- x[!y,]
y <- as.data.frame(t(apply(x[,c(1,2)], 1, sort)))
x <- x[! duplicated(y),]

ppi.graph = graph.data.frame(x[,c(1:2)],directed=F)
ppi.graph
adj.PPIonline <- as.matrix(get.adjacency(ppi.graph))
```

Running deconvolution normalization
```{r, echo=TRUE, message=FALSE, warning=FALSE}
# scran Normalization

# ---- Packages ----
library('DESeq2')
library('edgeR')
library('scran')
source("./functions.R") 


# ---- Data ----
emat <- emat[-c(93:109),]
sce <- newSCESet(countData=data.frame(emat))
#sce <- calculateQCMetrics(sce, feature_controls=list(MySpikes=(grepl("ERCC-",rownames(emat))),MyMit=(grepl("Mt_*", rownames(emat)))))
isSpike(sce) <- grepl("ERCC-",rownames(emat))
sce <- computeSumFactors(sce)
sce <- computeSpikeFactors(sce)
summary(sizeFactors(sce))
sce <- normalize(sce)

tmp <- convertTo(sce, type="monocle")
colnames(tmp) <- colnames(emat)
emat.normalized <- as.data.frame(exprs(tmp))
```
Now we calculate the entropy using the PPI network instead of the WGCNA network
```{r}
exp.m <- emat[-c(1:109),row.names(annotable_backSPIN)]
exp.m <- exp.m[apply(exp.m,1,function(x) any ((x) > 0)),]
exp.m <- log(exp.m+1)
ppiA.m <- adj.PPIonline
pheno.v <- annotable_backSPIN[,14]
names(pheno.v) <- row.names(annotable_backSPIN)
# First integrate exp.m and ppiA.m:
int.o.online <- DoIntegPPI(exp.m,ppiA.m)
# Now estimate maximum SR:
maxSR.online <- CompMaxSR(int.o.online$adjMC);
#Now estimate signaling entropies of all samples
SR.v.online <- vector(); for(s in 1:ncol(exp.m))
{SR.v.online[s] <- CompSRana(int.o.online$expMC[,s],int.o.online$adjMC,maxSR=maxSR.online)$sr; print(paste(100*(s/(ncol(exp.m)))));}
#Now perform SCENT:
scent.o.online2 <- DoSCENT(exp.m,sr.v=SR.v.online,pheno.v)
#Define bulk expression profile
expBLK.v.online <- rowMeans(int.o.online$expMC);
#Compute SR for bulk
SRblk.online <- CompSRana(expBLK.v.online,int.o.online$adjMC,maxSR=maxSR.online)
#Estimate MRH:
mrh.o.online <- EstMRH(SR.v.online,SRblk.online$sr);
View(scent.o.online$potS)
plot(density(scent.o.online$distPSPH))
anyNA(SR.v)
```

```{r, echo=FALSE}
#Show Entropy score
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=SR.v)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
#Show Entropy score
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=SR.v.online)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") +
  xlab("tSNE_1") + ylab("tSNE_2")
```
